---
title: "Marriage License Statistics Research"
subtitle: "A statistical approach to examine the effect of COVID-19 on marriage license rates in Toronto."
author: 
  - Bruce Zhang
thanks: "Code and data are available at: LINK."
date: 19 September 2024
date-format: long
abstract: "This is an abstract of this research article."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(opendatatoronto)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of marriage licenses (@fig-marriage). 

```{r}
#| label: fig-marriage
#| fig-cap: Marriage Licenses Relative to Time
#| echo: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

ggplot(data = analysis_data, mapping = aes(x = date, y = marriage_licenses)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Date", y = "Marriage Licences")
```

This graph shows the number of marriage licenses obtained relative to the date in Toronto. 

# Discussion

This section discusses the implications of the marriage data with regard to COVID-19. 

## First discussion point {#sec-first-point}

The dip around 2020 shows a decrease in marriage licensing shows the affect of COVID-19. There was a decreased marriage licensing rate during those times. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

The data used did not provided dates, only months and years were available. A better representation could be possible if exact dates were present. 

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics


\newpage


# References


